\title{Maximizing the impact of limited vaccine supply under different early epidemic conditions:
  a 2-city modelling analysis of monkeypox virus transmission among men who have sex with men}
\author[1,2]{Jesse Knight}
\author[1,2,3,4]{Darrell H.S. Tan}
\author[1,2,3,4]{Sharmistha Mishra}
\affil[1]{MAP Centre for Urban Health Solutions, Unity Health Toronto}
\affil[2]{Institute of Medical Science, University of Toronto}
\affil[3]{Institute of Health Policy, Management, and Evaluation, University of Toronto}
\affil[4]{Division of Infectious Diseases, Department of Medicine, University of Toronto}
\date{2022 Nov 28}
\journal{CMAJ}
\abstract{\input{abstract}}
\data{
All analysis code is available at \hreftt{github.com/mishra-lab/mpox-model-compartmental}.
Figures and numeric results can be obtained directly from this code using R.}
\funding{
The study was supported by:
the Natural Sciences and Engineering Research Council of Canada (NSERC CGS-D); and
the University of Toronto Emerging and Pandemic Infections Consortium (EPIC)
MPXV Collaborative Rapid Research Response.
No funder had any direct role in the research.
Sharmistha Mishra is supported by a Tier 2 Canada Research Chair in Mathematical Modeling and Program Science.
Darrell Tan is supported by a Tier 2 Canada Research Chair in HIV Prevention and STI Research.}
\acknowl{
The authors thank:
Kristy Yiu (Unity Health Toronto) for research coordination support;
Huiting Ma, Linwei Wang, Oliver Gatalo and Ekta Mishra (Unity Health Toronto)
for support with conceptualizing and parameterizing the model; and
Mackenzie Hamilton (Unity Health Toronto) for her feedback on the manuscript.
We also thank Toronto Public Health and members of the MPox Community Mobilization Group
for their insights, ongoing engagement, and feedback on preliminary results.}
\contrib{
JK and SM conceptualized and designed the study, and drafted the manuscript.
JK developed the model, conducted the analyses and generated the results.
SM and DT provided key interpretation of the results. 
DT contributed critical review of the manuscript.
All authors contributed to addressing revisions,
gave final approval of the version to be published,
and agreed to be accountable for all aspects of the work.}
